Plot previous findings

### 2024-07-13 code_data/previous_studies/PreviousFindings.Rmd
Updated via the Open Science Framework

## non sig. Sem effect in E2 crit region TFT:
VD07E2critSemTFTmn <- (761+653)/2-(738+630)/2
VD07E2critSemTFTtval <- 1.95 # reported as non-sig.
VD07E2critSemTFTSE <- VD07E2critSemTFTmn/VD07E2critSemTFTtval
VD07E2critSemTFTlower <- round(VD07E2critSemTFTmn - 2*VD07E2critSemTFTSE)
VD07E2critSemTFTupper <- round(VD07E2critSemTFTmn + 2*VD07E2critSemTFTSE)
```

@@

## non sig. Int effect in E2 crit region FPRT:
VD07E2critIntFPRTmn <- (418-413)-(382-376)
VD07E2critIntFPRTtval <- 1.95 # reported as non-sig.
VD07E2critIntFPRTSE <- VD07E2critIntFPRTmn/VD07E2critIntFPRTtval
VD07E2critIntFPRTlower <- round(VD07E2critIntFPRTmn - 2*VD07E2critIntFPRTSE)
VD07E2critIntFPRTupper <- round(VD07E2critIntFPRTmn + 2*VD07E2critIntFPRTSE)

# non sig. Int effect in E2 crit region RPD:
VD07E2critIntRPDmn <- (663-594)-(495-454)
VD07E2critIntRPDtval <- 1.95 # reported as non-sig.
VD07E2critIntRPDSE <- VD07E2critIntRPDmn/VD07E2critIntRPDtval
VD07E2critIntRPDlower <- round(VD07E2critIntRPDmn - 2*VD07E2critIntRPDSE)
VD07E2critIntRPDupper <- round(VD07E2critIntRPDmn + 2*VD07E2critIntRPDSE)

## non sig. Int effect in E2 crit region TFT:
VD07E2critIntTFTmn <- (761-738)-(653-630)
VD07E2critIntTFTtval <- 1.95 # reported as non-sig.
VD07E2critIntTFTSE <- VD07E2critIntTFTmn/VD07E2critIntTFTtval
VD07E2critIntTFTlower <- round(VD07E2critIntTFTmn - 2*VD07E2critIntTFTSE)
VD07E2critIntTFTupper <- round(VD07E2critIntTFTmn + 2*VD07E2critIntTFTSE)
```

@@

## non sig. Syn effect in E2 post-crit region TFT:
VD07E2postcritSynTFTmn <- (491+493)/2-(502+540)/2
VD07E2postcritSynTFTtval <- 1.95 # reported in paper as non-sig
VD07E2postcritSynTFTSE<- VD07E2postcritSynTFTmn/VD07E2postcritSynTFTtval
VD07E2postcritSynTFTlower <- round(VD07E2postcritSynTFTmn - 2*VD07E2postcritSynTFTSE)
VD07E2postcritSynTFTupper <- round(VD07E2postcritSynTFTmn + 2*VD07E2postcritSynTFTSE)
```

@@

## almost sig. Sem effect in E2 post-crit region FPRT (negative sign)
VD07E2postcritSemFPRTmn<- (296+364)/2-(325+320)/2
VD07E2postcritSemFPRTtval<- 1.95 # reported in paper as non-sig
VD07E2postcritSemFPRTSE<-VD07E2postcritSemFPRTmn/VD07E2postcritSemFPRTtval
VD07E2postcritSemFPRTlower<-VD07E2postcritSemFPRTmn-2*VD07E2postcritSemFPRTSE
VD07E2postcritSemFPRTupper<-VD07E2postcritSemFPRTmn+2*VD07E2postcritSemFPRTSE

## almost sig. Sem effect in E2 post-crit region RPD:
VD07E2postcritSemRPDmn <- (1295+1205)/2-(1365+970)/2
VD07E2postcritSemRPDtval <- 1.95 # reported in paper as non-sig
VD07E2postcritSemRPDSE <- VD07E2postcritSemRPDmn/VD07E2postcritSemRPDtval
VD07E2postcritSemRPDlower <- round(VD07E2postcritSemRPDmn - 2*VD07E2postcritSemRPDSE)
VD07E2postcritSemRPDupper <- round(VD07E2postcritSemRPDmn + 2*VD07E2postcritSemRPDSE)

## almost sig. Sem effect in E2 post-crit region TFT:
VD07E2postcritSemTFTmn <- (493+540)/2-(491+502)/2
VD07E2postcritSemTFTtval <- 1.95 # reported in paper as non-sig
VD07E2postcritSemTFTSE <- VD07E2postcritSemTFTmn/VD07E2postcritSemTFTtval
VD07E2postcritSemTFTlower <- round(VD07E2postcritSemTFTmn - 2*VD07E2postcritSemTFTSE)
VD07E2postcritSemTFTupper <- round(VD07E2postcritSemTFTmn + 2*VD07E2postcritSemTFTSE)
```

@@

## almost sig. Int effect in E2 post-crit region TFT:
VD07E2postcritIntTFTmn <- (493-491)-(540-502)
VD07E2postcritIntTFTtval <- 1.95 # reported in paper as non-sig
VD07E2postcritIntTFTSE <-  VD07E2postcritIntTFTmn/VD07E2postcritIntTFTtval
VD07E2postcritIntTFTlower <- round(VD07E2postcritIntTFTmn - 2*VD07E2postcritIntTFTSE)
VD07E2postcritIntTFTupper <- round(VD07E2postcritIntTFTmn + 2*VD07E2postcritIntTFTSE)
```

@@

## Syn effect in E2 sentence-final region FPRT 
VD07E2finalSynFPRTmn<-(259+271)/2-(286+274)/2
VD07E2finalSynFPRTtval<- 1.95 # reported in paper as non-sig
VD07E2finalSynFPRTSE<-VD07E2finalSynFPRTmn/VD07E2finalSynFPRTtval
VD07E2finalSynFPRTlower<-VD07E2finalSynFPRTmn-2*VD07E2finalSynFPRTSE
VD07E2finalSynFPRTupper<-VD07E2finalSynFPRTmn+2*VD07E2finalSynFPRTSE

@@

## Syn effect in E2 sentence-final region TFT:
VD07E2finalSynTFTmn <- (349+360)/2-(362+373)/2
VD07E2finalSynTFTtval <- 1.95 # reported in paper as non-sig
VD07E2finalSynTFTSE<- VD07E2finalSynTFTmn/VD07E2finalSynTFTtval
VD07E2finalSynTFTlower <- round(VD07E2finalSynTFTmn - 2*VD07E2finalSynTFTSE)
VD07E2finalSynTFTupper <- round(VD07E2finalSynTFTmn + 2*VD07E2finalSynTFTSE)
```

@@

## Sem effect in E2 sentence-final region FPRT
VD07E2finalSemFPRTmn<- (271+274)/2-(259+286)/2
VD07E2finalSemFPRTtval<- 1.95 # reported in paper as non-sig
VD07E2finalSemFPRTSE<-VD07E2finalSemFPRTmn/VD07E2finalSemFPRTtval
VD07E2finalSemFPRTlower<-VD07E2finalSemFPRTmn-2*VD07E2finalSemFPRTSE
VD07E2finalSemFPRTupper<-VD07E2finalSemFPRTmn+2*VD07E2finalSemFPRTSE

@@

## Sem effect in E2 sentence-final region TFT:
VD07E2finalSemTFTmn <- (360+373)/2-(349+362)/2
VD07E2finalSemTFTtval <- 1.95 # reported in paper as non-sig
VD07E2finalSemTFTSE <- VD07E2finalSemTFTmn/VD07E2finalSemTFTtval
VD07E2finalSemTFTlower <- round(VD07E2finalSemTFTmn - 2*VD07E2finalSemTFTSE)
VD07E2finalSemTFTupper <- round(VD07E2finalSemTFTmn + 2*VD07E2finalSemTFTSE)
```

@@

## Int effect in E2 sentence-final region FPRT
VD07E2finalIntFPRTmn<- (271-259)-(274-286)
VD07E2finalIntFPRTtval<- 1.95 # reported in paper as non-sig
VD07E2finalIntFPRTSE<-VD07E2finalIntFPRTmn/VD07E2finalIntFPRTtval
VD07E2finalIntFPRTlower<-VD07E2finalIntFPRTmn-2*VD07E2finalIntFPRTSE
VD07E2finalIntFPRTupper<-VD07E2finalIntFPRTmn+2*VD07E2finalIntFPRTSE

@@

## Int effect in E2 sentence-final region TFT:
VD07E2finalIntTFTmn <- (360-349)-(373-362)
VD07E2finalIntTFTtval <- 1.95 # reported in paper as non-sig
VD07E2finalIntTFTSE <-  VD07E2finalIntTFTmn/VD07E2finalIntTFTtval
VD07E2finalIntTFTlower <- round(VD07E2finalIntTFTmn - 2*VD07E2finalIntTFTSE)
VD07E2finalIntTFTupper <- round(VD07E2finalIntTFTmn + 2*VD07E2finalIntTFTSE)
```

@@

## almost sig. Syn effect in E3 precrit region FPRT:
VD07E3precritSynFPRTmn <- (462+447)/2-(449+455)/2
VD07E3precritSynFPRTtval <- 1.95 # reported in paper as non-sig
VD07E3precritSynFPRTSE <- VD07E3precritSynFPRTmn/VD07E3precritSynFPRTtval
VD07E3precritSynFPRTlower <- round(VD07E3precritSynFPRTmn-2*VD07E3precritSynFPRTSE)
VD07E3precritSynFPRTupper <- round(VD07E3precritSynFPRTmn+2*VD07E3precritSynFPRTSE)

@@

## almost sig. Sem effect in E3 precrit region FPRT:
VD07E3precritSemFPRTmn <- (455+447)/2-(449+462)/2
VD07E3precritSemFPRTtval <- 1.95 # reported in paper as non-sig
VD07E3precritSemFPRTSE <- VD07E3precritSemFPRTmn/VD07E3precritSemFPRTtval
VD07E3precritSemFPRTlower <- round(VD07E3precritSemFPRTmn-2*VD07E3precritSemFPRTSE)
VD07E3precritSemFPRTupper <- round(VD07E3precritSemFPRTmn+2*VD07E3precritSemFPRTSE)

@@

## almost sig. Int effect in E3 precrit region FPRT:
VD07E3precritIntFPRTmn <- (447-462)-(455-449)
VD07E3precritIntFPRTtval <- 1.95 # reported in paper as non-sig
VD07E3precritIntFPRTSE <- VD07E3precritIntFPRTmn/VD07E3precritIntFPRTtval
VD07E3precritIntFPRTlower <- round(VD07E3precritIntFPRTmn-2*VD07E3precritIntFPRTSE)
VD07E3precritIntFPRTupper <- round(VD07E3precritIntFPRTmn+2*VD07E3precritIntFPRTSE)

## almost sig. Int effect in E3 precrit region RPD:
VD07E3precritIntRPDmn <- (551-490)-(493-472)
VD07E3precritIntRPDtval <- 1.95 # reported in paper as non-sig
VD07E3precritIntRPDSE <- VD07E3precritIntRPDmn/VD07E3precritIntRPDtval
VD07E3precritIntRPDlower <- round(VD07E3precritIntRPDmn-2*VD07E3precritIntRPDSE)
VD07E3precritIntRPDupper <- round(VD07E3precritIntRPDmn+2*VD07E3precritIntRPDSE)

## almost sig. Int effect in E3 precrit region TFT:
VD07E3precritIntTFTmn <- (710-622)-(640-586)
VD07E3precritIntTFTtval <- 1.95 # reported in paper as non-sig
VD07E3precritIntTFTSE <- VD07E3precritIntTFTmn/VD07E3precritIntTFTtval
VD07E3precritIntTFTlower <- round(VD07E3precritIntTFTmn-2*VD07E3precritIntTFTSE)
VD07E3precritIntTFTupper <- round(VD07E3precritIntTFTmn+2*VD07E3precritIntTFTSE)
```

@@

## almost sig. Syn effect in E3 crit region TFT:
VD07E3critSynTFTmn <- (451+467)/2-(414+421)/2
VD07E3critSynTFTtval <- 1.95 # reported in paper as non-sig
VD07E3critSynTFTSE <- VD07E3critSynTFTmn/VD07E3critSynTFTtval
VD07E3critSynTFTlower <- round(VD07E3critSynTFTmn-2*VD07E3critSynTFTSE)
VD07E3critSynTFTupper <- round(VD07E3critSynTFTmn+2*VD07E3critSynTFTSE)

@@

## almost sig. Sem effect in E3 crit region FPRT:
VD07E3critSemFPRTmn <- (282+280)/2-(274+294)/2
VD07E3critSemFPRTtval <- 1.95 # reported in paper as non-sig
VD07E3critSemFPRTSE <- VD07E3critSemFPRTmn/VD07E3critSemFPRTtval
VD07E3critSemFPRTlower <- round(VD07E3critSemFPRTmn-2*VD07E3critSemFPRTSE)
VD07E3critSemFPRTupper <- round(VD07E3critSemFPRTmn+2*VD07E3critSemFPRTSE)

## almost sig. Sem effect in E3 crit region RPD:
VD07E3critSemRPDmn <- (315+344)/2-(314+354)/2
VD07E3critSemRPDtval <- 1.95 # reported in paper as non-sig
VD07E3critSemRPDSE <- VD07E3critSemRPDmn/VD07E3critSemRPDtval
VD07E3critSemRPDlower <- round(VD07E3critSemRPDmn-2*VD07E3critSemRPDSE)
VD07E3critSemRPDupper <- round(VD07E3critSemRPDmn+2*VD07E3critSemRPDSE)

## almost sig. Sem effect in E3 crit region TFT:
VD07E3critSemTFTmn <- (421+467)/2-(414+451)/2
VD07E3critSemTFTtval <- 1.95 # reported in paper as non-sig
VD07E3critSemTFTSE <- VD07E3critSemTFTmn/VD07E3critSemTFTtval
VD07E3critSemTFTlower <- round(VD07E3critSemTFTmn-2*VD07E3critSemTFTSE)
VD07E3critSemTFTupper <- round(VD07E3critSemTFTmn+2*VD07E3critSemTFTSE)
```

@@

## almost sig. Int effect in E3 crit region RPD:
VD07E3critIntRPDmn <- (344-354)-(315-314)
VD07E3critIntRPDtval <- 1.95 # reported in paper as non-sig
VD07E3critIntRPDSE <- VD07E3critIntRPDmn/VD07E3critIntRPDtval
VD07E3critIntRPDlower <- round(VD07E3critIntRPDmn-2*VD07E3critIntRPDSE)
VD07E3critIntRPDupper <- round(VD07E3critIntRPDmn+2*VD07E3critIntRPDSE)

## almost sig. Int effect in E3 crit region TFT:
VD07E3critIntTFTmn <- (467-451)-(421-414)
VD07E3critIntTFTtval <- 1.95 # reported in paper as non-sig
VD07E3critIntTFTSE <- VD07E3critIntTFTmn/VD07E3critIntTFTtval
VD07E3critIntTFTlower <- round(VD07E3critIntTFTmn-2*VD07E3critIntTFTSE)
VD07E3critIntTFTupper <- round(VD07E3critIntTFTmn+2*VD07E3critIntTFTSE)
```

@@

## almost sig. Syn effect in E3 postcrit region FPRT:
VD07E3postcritSynFPRTmn <- (424+442)/2-(437+448)/2
VD07E3postcritSynFPRTtval <- 1.95 # reported in paper as non-sig
VD07E3postcritSynFPRTSE <- VD07E3postcritSynFPRTmn/VD07E3postcritSynFPRTtval
VD07E3postcritSynFPRTlower <- round(VD07E3postcritSynFPRTmn-2*VD07E3postcritSynFPRTSE)
VD07E3postcritSynFPRTupper <- round(VD07E3postcritSynFPRTmn+2*VD07E3postcritSynFPRTSE)

@@

## almost sig. Syn effect in E3 postcrit region TFT:
VD07E3postcritSynTFTmn <- (766+731)/2-(707+711)/2
VD07E3postcritSynTFTtval <- 1.95 # reported in paper as non-sig
VD07E3postcritSynTFTSE <- VD07E3postcritSynTFTmn/VD07E3postcritSynTFTtval
VD07E3postcritSynTFTlower <- round(VD07E3postcritSynTFTmn-2*VD07E3postcritSynTFTSE)
VD07E3postcritSynTFTupper <- round(VD07E3postcritSynTFTmn+2*VD07E3postcritSynTFTSE)

@@

## almost sig. Sem effect in E3 postcrit region FPRT:
VD07E3postcritSemFPRTmn <- (437+424)/2-(448+442)/2
VD07E3postcritSemFPRTtval <- 1.95 # reported in paper as non-sig
VD07E3postcritSemFPRTSE <- VD07E3postcritSemFPRTmn/VD07E3postcritSemFPRTtval
VD07E3postcritSemFPRTlower <- round(VD07E3postcritSemFPRTmn-2*VD07E3postcritSemFPRTSE)
VD07E3postcritSemFPRTupper <- round(VD07E3postcritSemFPRTmn+2*VD07E3postcritSemFPRTSE)

@@

## almost sig. Int effect in E3 postcrit region FPRT:
VD07E3postcritIntFPRTmn <- (424-442)-(437-448)
VD07E3postcritIntFPRTtval <- 1.95 # reported in paper as non-sig
VD07E3postcritIntFPRTSE <- VD07E3postcritIntFPRTmn/VD07E3postcritIntFPRTtval
VD07E3postcritIntFPRTlower <- round(VD07E3postcritIntFPRTmn-2*VD07E3postcritIntFPRTSE)
VD07E3postcritIntFPRTupper <- round(VD07E3postcritIntFPRTmn+2*VD07E3postcritIntFPRTSE)

## almost sig. Int effect in E3 postcrit region RPD:
VD07E3postcritIntRPDmn <- (615-625)-(553-607)
VD07E3postcritIntRPDtval <- 1.95 # reported in paper as non-sig
VD07E3postcritIntRPDSE <- VD07E3postcritIntRPDmn/VD07E3postcritIntRPDtval
VD07E3postcritIntRPDlower <- round(VD07E3postcritIntRPDmn-2*VD07E3postcritIntRPDSE)
VD07E3postcritIntRPDupper <- round(VD07E3postcritIntRPDmn+2*VD07E3postcritIntRPDSE)

## almost sig. Int effect in E3 postcrit region TFT:
VD07E3postcritIntTFTmn <- (766-731)-(707-711)
VD07E3postcritIntTFTtval <- 1.95 # reported in paper as non-sig
VD07E3postcritIntTFTSE <- VD07E3postcritIntTFTmn/VD07E3postcritIntTFTtval
VD07E3postcritIntTFTlower <- round(VD07E3postcritIntTFTmn-2*VD07E3postcritIntTFTSE)
VD07E3postcritIntTFTupper <- round(VD07E3postcritIntTFTmn+2*VD07E3postcritIntTFTSE)
```

@@

# combine with previous estimates
estimates <- rbind(previous, SVestimates)

@@

pp.plot + coord_cartesian(ylim=c(-25, 75))  
ggsave("plots/present_previous_findings.jpg", width=9, height=8, dpi=600)

@@

>>>>

## non sig. Sem effect in E2 crit region TFT:
VD07E2critSemTFTmn <- (761+653)/2-(738+630)/2
VD07E2critSemTFTSE <- 42 #highest SE in critical region, Table 7
VD07E2critSemTFTlower <- round(VD07E2critSemTFTmn - 2*VD07E2critSemTFTSE)
VD07E2critSemTFTupper <- round(VD07E2critSemTFTmn + 2*VD07E2critSemTFTSE)
```

@@

## non sig. Int effect in E2 crit region FPRT:
VD07E2critIntFPRTmn <- (418-413)-(382-376)
VD07E2critIntFPRTSE <- 21 #highest SE in critical region, Table 7
VD07E2critIntFPRTlower <- round(VD07E2critIntFPRTmn - 2*VD07E2critIntFPRTSE)
VD07E2critIntFPRTupper <- round(VD07E2critIntFPRTmn + 2*VD07E2critIntFPRTSE)

# non sig. Int effect in E2 crit region RPD:
VD07E2critIntRPDmn <- (663-594)-(495-454)
VD07E2critIntRPDSE <- 44 #highest SE in critical region, Table 7
VD07E2critIntRPDlower <- round(VD07E2critIntRPDmn - 2*VD07E2critIntRPDSE)
VD07E2critIntRPDupper <- round(VD07E2critIntRPDmn + 2*VD07E2critIntRPDSE)

## non sig. Int effect in E2 crit region TFT:
VD07E2critIntTFTmn <- (761-738)-(653-630)
VD07E2critIntTFTSE <- 42 #highest SE in critical region, Table 7
VD07E2critIntTFTlower <- round(VD07E2critIntTFTmn - 2*VD07E2critIntTFTSE)
VD07E2critIntTFTupper <- round(VD07E2critIntTFTmn + 2*VD07E2critIntTFTSE)
```

@@

## non sig. Syn effect in E2 post-crit region TFT:
VD07E2postcritSynTFTmn <- (491+493)/2-(502+540)/2
VD07E2postcritSynTFTSE <- 30 #highest SE in spill-over region, Table 7
VD07E2postcritSynTFTlower <- round(VD07E2postcritSynTFTmn - 2*VD07E2postcritSynTFTSE)
VD07E2postcritSynTFTupper <- round(VD07E2postcritSynTFTmn + 2*VD07E2postcritSynTFTSE)
```

@@

## almost sig. Sem effect in E2 post-crit region FPRT (negative sign)
VD07E2postcritSemFPRTmn<- (296+364)/2-(325+320)/2
VD07E2postcritSemFPRTSE<- 21 #highest SE in spill-over region, Table 7
VD07E2postcritSemFPRTlower<-VD07E2postcritSemFPRTmn-2*VD07E2postcritSemFPRTSE
VD07E2postcritSemFPRTupper<-VD07E2postcritSemFPRTmn+2*VD07E2postcritSemFPRTSE

## almost sig. Sem effect in E2 post-crit region RPD:
VD07E2postcritSemRPDmn <- (1295+1205)/2-(1365+970)/2
VD07E2postcritSemRPDSE <- 140 #highest SE in spill-over region, Table 7
VD07E2postcritSemRPDlower <- round(VD07E2postcritSemRPDmn - 2*VD07E2postcritSemRPDSE)
VD07E2postcritSemRPDupper <- round(VD07E2postcritSemRPDmn + 2*VD07E2postcritSemRPDSE)

## almost sig. Sem effect in E2 post-crit region TFT:
VD07E2postcritSemTFTmn <- (493+540)/2-(491+502)/2
VD07E2postcritSemTFTSE <-  30 #highest SE in spill-over region, Table 7
VD07E2postcritSemTFTlower <- round(VD07E2postcritSemTFTmn - 2*VD07E2postcritSemTFTSE)
VD07E2postcritSemTFTupper <- round(VD07E2postcritSemTFTmn + 2*VD07E2postcritSemTFTSE)
```

@@

## almost sig. Int effect in E2 post-crit region TFT:
VD07E2postcritIntTFTmn <- (493-491)-(540-502)
VD07E2postcritIntTFTSE <- 30 #highest SE in spill-over region, Table 7
VD07E2postcritIntTFTlower <- round(VD07E2postcritIntTFTmn - 2*VD07E2postcritIntTFTSE)
VD07E2postcritIntTFTupper <- round(VD07E2postcritIntTFTmn + 2*VD07E2postcritIntTFTSE)
```

@@

## Syn effect in E2 sentence-final region FPRT 
VD07E2finalSynFPRTmn<-(259+271)/2-(286+274)/2
VD07E2finalSynFPRTSE<- 22 #highest SE in sentence-final region, Table 7
VD07E2finalSynFPRTlower<-VD07E2finalSynFPRTmn-2*VD07E2finalSynFPRTSE
VD07E2finalSynFPRTupper<-VD07E2finalSynFPRTmn+2*VD07E2finalSynFPRTSE

@@

## Syn effect in E2 sentence-final region TFT:
VD07E2finalSynTFTmn <- (349+360)/2-(362+373)/2
VD07E2finalSynTFTSE<- 40 #highest SE in sentence-final region, Table 7
VD07E2finalSynTFTlower <- round(VD07E2finalSynTFTmn - 2*VD07E2finalSynTFTSE)
VD07E2finalSynTFTupper <- round(VD07E2finalSynTFTmn + 2*VD07E2finalSynTFTSE)
```

@@

## Sem effect in E2 sentence-final region FPRT
VD07E2finalSemFPRTmn<- (271+274)/2-(259+286)/2
VD07E2finalSemFPRTSE<- 22 #highest SE in sentence-final region, Table 7
VD07E2finalSemFPRTlower<-VD07E2finalSemFPRTmn-2*VD07E2finalSemFPRTSE
VD07E2finalSemFPRTupper<-VD07E2finalSemFPRTmn+2*VD07E2finalSemFPRTSE

@@

## Sem effect in E2 sentence-final region TFT:
VD07E2finalSemTFTmn <- (360+373)/2-(349+362)/2
VD07E2finalSemTFTSE <- 40 #highest SE in sentence-final region, Table 7
VD07E2finalSemTFTlower <- round(VD07E2finalSemTFTmn - 2*VD07E2finalSemTFTSE)
VD07E2finalSemTFTupper <- round(VD07E2finalSemTFTmn + 2*VD07E2finalSemTFTSE)
```

@@

## Int effect in E2 sentence-final region FPRT
VD07E2finalIntFPRTmn<- (271-259)-(274-286)
VD07E2finalIntFPRTSE<- 22 #highest SE in sentence-final region, Table 7
VD07E2finalIntFPRTlower<-VD07E2finalIntFPRTmn-2*VD07E2finalIntFPRTSE
VD07E2finalIntFPRTupper<-VD07E2finalIntFPRTmn+2*VD07E2finalIntFPRTSE

@@

## Int effect in E2 sentence-final region TFT:
VD07E2finalIntTFTmn <- (360-349)-(373-362)
VD07E2finalIntTFTSE <-  40 #highest SE in sentence-final region, Table 7
VD07E2finalIntTFTlower <- round(VD07E2finalIntTFTmn - 2*VD07E2finalIntTFTSE)
VD07E2finalIntTFTupper <- round(VD07E2finalIntTFTmn + 2*VD07E2finalIntTFTSE)
```

@@

## almost sig. Syn effect in E3 precrit region FPRT:
VD07E3precritSynFPRTmn <- (462+447)/2-(449+455)/2
VD07E3precritSynFPRTSE <- 18 #highest SE in pre-crit region, Table 16
VD07E3precritSynFPRTlower <- round(VD07E3precritSynFPRTmn-2*VD07E3precritSynFPRTSE)
VD07E3precritSynFPRTupper <- round(VD07E3precritSynFPRTmn+2*VD07E3precritSynFPRTSE)

@@

## almost sig. Sem effect in E3 precrit region FPRT:
VD07E3precritSemFPRTmn <- (455+447)/2-(449+462)/2
VD07E3precritSemFPRTSE <- 18 #highest SE in pre-crit region, Table 16
VD07E3precritSemFPRTlower <- round(VD07E3precritSemFPRTmn-2*VD07E3precritSemFPRTSE)
VD07E3precritSemFPRTupper <- round(VD07E3precritSemFPRTmn+2*VD07E3precritSemFPRTSE)

@@

## almost sig. Int effect in E3 precrit region FPRT:
VD07E3precritIntFPRTmn <- (447-462)-(455-449)
VD07E3precritIntFPRTSE <- 18 #highest SE in pre-crit region, Table 16
VD07E3precritIntFPRTlower <- round(VD07E3precritIntFPRTmn-2*VD07E3precritIntFPRTSE)
VD07E3precritIntFPRTupper <- round(VD07E3precritIntFPRTmn+2*VD07E3precritIntFPRTSE)

## almost sig. Int effect in E3 precrit region RPD:
VD07E3precritIntRPDmn <- (551-490)-(493-472)
VD07E3precritIntRPDSE <- 36 #highest SE in pre-crit region, Table 16
VD07E3precritIntRPDlower <- round(VD07E3precritIntRPDmn-2*VD07E3precritIntRPDSE)
VD07E3precritIntRPDupper <- round(VD07E3precritIntRPDmn+2*VD07E3precritIntRPDSE)

## almost sig. Int effect in E3 precrit region TFT:
VD07E3precritIntTFTmn <- (710-622)-(640-586)
VD07E3precritIntTFTSE <- 47 #highest SE in pre-crit region, Table 16
VD07E3precritIntTFTlower <- round(VD07E3precritIntTFTmn-2*VD07E3precritIntTFTSE)
VD07E3precritIntTFTupper <- round(VD07E3precritIntTFTmn+2*VD07E3precritIntTFTSE)
```

@@

## almost sig. Syn effect in E3 crit region TFT:
VD07E3critSynTFTmn <- (451+467)/2-(414+421)/2
VD07E3critSynTFTSE <- 38 #highest SE in crit region, Table 16
VD07E3critSynTFTlower <- round(VD07E3critSynTFTmn-2*VD07E3critSynTFTSE)
VD07E3critSynTFTupper <- round(VD07E3critSynTFTmn+2*VD07E3critSynTFTSE)

@@

## almost sig. Sem effect in E3 crit region FPRT:
VD07E3critSemFPRTmn <- (282+280)/2-(274+294)/2
VD07E3critSemFPRTSE <- 11 #highest SE in crit region, Table 16
VD07E3critSemFPRTlower <- round(VD07E3critSemFPRTmn-2*VD07E3critSemFPRTSE)
VD07E3critSemFPRTupper <- round(VD07E3critSemFPRTmn+2*VD07E3critSemFPRTSE)

## almost sig. Sem effect in E3 crit region RPD:
VD07E3critSemRPDmn <- (315+344)/2-(314+354)/2
VD07E3critSemRPDSE <- 23 #highest SE in crit region, Table 16
VD07E3critSemRPDlower <- round(VD07E3critSemRPDmn-2*VD07E3critSemRPDSE)
VD07E3critSemRPDupper <- round(VD07E3critSemRPDmn+2*VD07E3critSemRPDSE)

## almost sig. Sem effect in E3 crit region TFT:
VD07E3critSemTFTmn <- (421+467)/2-(414+451)/2
VD07E3critSemTFTSE <- 38 #highest SE in crit region, Table 16
VD07E3critSemTFTlower <- round(VD07E3critSemTFTmn-2*VD07E3critSemTFTSE)
VD07E3critSemTFTupper <- round(VD07E3critSemTFTmn+2*VD07E3critSemTFTSE)
```

@@

## almost sig. Int effect in E3 crit region RPD:
VD07E3critIntRPDmn <- (344-354)-(315-314)
VD07E3critIntRPDSE <- 23 #highest SE in crit region, Table 16
VD07E3critIntRPDlower <- round(VD07E3critIntRPDmn-2*VD07E3critIntRPDSE)
VD07E3critIntRPDupper <- round(VD07E3critIntRPDmn+2*VD07E3critIntRPDSE)

## almost sig. Int effect in E3 crit region TFT:
VD07E3critIntTFTmn <- (467-451)-(421-414)
VD07E3critIntTFTSE <- 38 #highest SE in crit region, Table 16
VD07E3critIntTFTlower <- round(VD07E3critIntTFTmn-2*VD07E3critIntTFTSE)
VD07E3critIntTFTupper <- round(VD07E3critIntTFTmn+2*VD07E3critIntTFTSE)
```

@@

## almost sig. Syn effect in E3 postcrit region FPRT:
VD07E3postcritSynFPRTmn <- (424+442)/2-(437+448)/2
VD07E3postcritSynFPRTSE <- 24 #highest SE in spill-over region, Table 16
VD07E3postcritSynFPRTlower <- round(VD07E3postcritSynFPRTmn-2*VD07E3postcritSynFPRTSE)
VD07E3postcritSynFPRTupper <- round(VD07E3postcritSynFPRTmn+2*VD07E3postcritSynFPRTSE)

@@

## almost sig. Syn effect in E3 postcrit region TFT:
VD07E3postcritSynTFTmn <- (766+731)/2-(707+711)/2
VD07E3postcritSynTFTSE <- 59 #highest SE in spill-over region, Table 16
VD07E3postcritSynTFTlower <- round(VD07E3postcritSynTFTmn-2*VD07E3postcritSynTFTSE)
VD07E3postcritSynTFTupper <- round(VD07E3postcritSynTFTmn+2*VD07E3postcritSynTFTSE)

@@

## almost sig. Sem effect in E3 postcrit region FPRT:
VD07E3postcritSemFPRTmn <- (437+424)/2-(448+442)/2
VD07E3postcritSemFPRTSE <- 24 #highest SE in spill-over region, Table 16
VD07E3postcritSemFPRTlower <- round(VD07E3postcritSemFPRTmn-2*VD07E3postcritSemFPRTSE)
VD07E3postcritSemFPRTupper <- round(VD07E3postcritSemFPRTmn+2*VD07E3postcritSemFPRTSE)

@@

## almost sig. Int effect in E3 postcrit region FPRT:
VD07E3postcritIntFPRTmn <- (424-442)-(437-448)
VD07E3postcritIntFPRTSE <-24 #highest SE in spill-over region, Table 16
VD07E3postcritIntFPRTlower <- round(VD07E3postcritIntFPRTmn-2*VD07E3postcritIntFPRTSE)
VD07E3postcritIntFPRTupper <- round(VD07E3postcritIntFPRTmn+2*VD07E3postcritIntFPRTSE)

## almost sig. Int effect in E3 postcrit region RPD:
VD07E3postcritIntRPDmn <- (615-625)-(553-607)
VD07E3postcritIntRPDSE <- 41 #highest SE in spill-over region, Table 16
VD07E3postcritIntRPDlower <- round(VD07E3postcritIntRPDmn-2*VD07E3postcritIntRPDSE)
VD07E3postcritIntRPDupper <- round(VD07E3postcritIntRPDmn+2*VD07E3postcritIntRPDSE)

## almost sig. Int effect in E3 postcrit region TFT:
VD07E3postcritIntTFTmn <- (766-731)-(707-711)
VD07E3postcritIntTFTSE <- 59 #highest SE in spill-over region, Table 16
VD07E3postcritIntTFTlower <- round(VD07E3postcritIntTFTmn-2*VD07E3postcritIntTFTSE)
VD07E3postcritIntTFTupper <- round(VD07E3postcritIntTFTmn+2*VD07E3postcritIntTFTSE)
```

@@

# combine with previous estimates
estimates <- rbind(previous, SVestimates)
estimates$experiment <- factor(estimates$experiment, levels=c("VD07.E1 (N=35)", "VD07.E2 (N=36)", "VD07.E3 (N=40)", "M23.E (N=61)", "M23.G (N=121)", "present (N=774)"))

@@

RTs.plot <- pp.plot + coord_cartesian(ylim=c(-75, 150)) + ggtitle("Reading time differences") 
ggsave("plots/present_previous_findings.jpg", width=9, height=8, dpi=600)

pp2.plot <- ggplot(data=filter(estimates, region %in% c("pre-critical", "critical", "spill-over") & measure %in%c("SPR", "TFT")),
                   aes(x=int_type, y=mean, ymin=lower, ymax=upper )) +
    geom_pointrange(aes(color=experiment, shape=measure), 
             size=0.8, position=position_dodge(1.45))+
  scale_shape_manual(values = c(18,16,17,15), breaks=c("SPR", "FPRT", "RPD", "TFT"),
                         labels=c("self-paced reading time", "first-pass reading time", "regression path duration", "total fixation time"))+
  scale_color_manual(values = c(my_colors[3], my_colors[4],my_colors[5],my_colors[8],my_colors[9], "black"))+
  geom_hline(yintercept=0, linetype="solid", alpha=.5)+
  facet_grid(region~int_type, scales="free", space="free") +
  theme_bw(base_size = 15)+
  scale_x_discrete(breaks = NULL)+
  theme(legend.position="right", legend.box="vertical", legend.direction="vertical")+
  xlab("")+
  ylab("reading time difference (ms)")+
  #ggtitle("Present and previous findings")+
  guides(shape = guide_legend(order = 2),col = guide_legend(order = 1))

pp2.plot + coord_cartesian(ylim=c(-50, 100))  
ggsave("plots/present_previous_findings_SPR_TFT.jpg", width=9, height=8, dpi=600)

@@

# Compute BF10 for Van Dyke (2007) data
```{r}
# function to compute BF10 repeatedly
compute_BF <- function(mean_effect, se){
